Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-10 paper.tex
np stuff

TODO NUMPY WRITE FATST HING

>>>>

Some drawbacks also include the use of the \verb|mpi4py| library instead of the MPI libraries in C++. Because \verb|mpi4py| is a set of Python bindings for MPI, based on the standard MPI-2 C++ bindings, there is additional overhead involved with mapping \verb|mpi4py| commands to the standard C++ library. For example, since Python is dynamically typed, additional information about size may first need to be sent as a part of the Python bindings, creating greater overhead as compared to the C++ libraries. In addition, C++ compilers may be more optimizable according to specific use case, as specific \verb|-o| flags or other compiler shortcuts may be specified directly, rather than through a standard wrapper class as provided by \verb|mpi4py|.

\textbf{something here about parareal? ashi}
